---
date: "4/27/2019"
output: pdf_document
---

```{r loading packages, eval=FALSE}
install.packages(c("rtweet", "tidytext", "httpuv", "ggplot2", "dplyr", "readr", "stringr", "tm", "hunspell", "wordcloud2"))
library(rtweet)
library(tidytext)
library(httpuv)
library(ggplot2)
library(dplyr)
library(readr)
library(stringr)
library(tm)
library(hunspell)
library(wordcloud2)

```

### GAMES DATA CLEAN-UP SECTION ###

##Auburn_vs_Kentucky
```{r Auburn_vs_Kentucky, eval=FALSE}
Auburn_vs_Kentucky_0331 = readRDS("Auburn_vs_Kentucky_0331.rds")

#Removing unwanted columns
Auburn_vs_Kentucky_0331_tidy = Auburn_vs_Kentucky_0331[, -c(7:12,16:60,67:69,86:88)]

#Adding a column named GameName
Auburn_vs_Kentucky_0331_tidy$GameName = c(rep("Auburn_vs_Kentucky", nrow(Auburn_vs_Kentucky_0331_tidy)))

#Rearranging the columns
Auburn_vs_Kentucky_0331_tidy = Auburn_vs_Kentucky_0331_tidy[,c(32,1:31)]

Auburn_vs_Kentucky_0331_tidy$timeinterval = cut(Auburn_vs_Kentucky_0331_tidy$created_at, breaks = "5 min")

#write_as_csv(Auburn_vs_Kentucky_0331_tidy, "Auburn_vs_Kentucky_0331_tidy.csv")
```

##Auburn_vs_Virginia
```{r Auburn_vs_Virginia, eval=FALSE}
Auburn_vs_Virginia_0406 = readRDS("Auburn_vs_Virginia_0406.rds")

#Removing unwanted columns
Auburn_vs_Virginia_0406_tidy = Auburn_vs_Virginia_0406[, -c(7:12,16:60,67:69,86:88)]

#Adding a column named GameName
Auburn_vs_Virginia_0406_tidy$GameName = c(rep("Auburn_vs_Virginia", nrow(Auburn_vs_Virginia_0406_tidy)))

#Rearranging the columns
Auburn_vs_Virginia_0406_tidy = Auburn_vs_Virginia_0406_tidy[,c(32,1:31)]

#Create timeinterval column
Auburn_vs_Virginia_0406_tidy$timeinterval = cut(Auburn_vs_Virginia_0406_tidy$created_at, breaks = "5 min")

#write_as_csv(Auburn_vs_Virginia_0406_tidy, "Auburn_vs_Virginia_0406_tidy.csv")
```

##VirginiaTech_vs_Duke
```{r VirginiaTech_vs_Duke, eval=FALSE}
VirginiaTech_vs_Duke_0329 = readRDS("VirginiaTech_vs_Duke_0329.rds")

#Removing unwanted columns
VirginiaTech_vs_Duke_0329_tidy = VirginiaTech_vs_Duke_0329[, -c(7:12,16:60,67:69,86:88)]

#Adding a column named GameName
VirginiaTech_vs_Duke_0329_tidy$GameName = c(rep("VirginiaTech_vs_Duke", nrow(VirginiaTech_vs_Duke_0329_tidy)))

#Rearranging the columns
VirginiaTech_vs_Duke_0329_tidy = VirginiaTech_vs_Duke_0329_tidy[,c(32,1:31)]

#Create timeinterval column
VirginiaTech_vs_Duke_0329_tidy$timeinterval = cut(VirginiaTech_vs_Duke_0329_tidy$created_at, breaks = "5 min")

#write_as_csv(VirginiaTech_vs_Duke_0329_tidy, "VirginiaTech_vs_Duke_0329_tidy.csv")
```

##TexasTech_vs_Michigan
```{r TexasTech_vs_Michigan_0328, eval=FALSE}
TexasTech_vs_Michigan_0328 = readRDS("TexasTech_vs_Michigan_0328.rds")

#Removing unwanted columns
TexasTech_vs_Michigan_0328_tidy = TexasTech_vs_Michigan_0328[, -c(7:12,16:60,67:69,86:88)]

#Adding a column named GameName
TexasTech_vs_Michigan_0328_tidy$GameName = c(rep("TexasTech_vs_Michigan", nrow(TexasTech_vs_Michigan_0328_tidy)))

#Rearranging the columns
TexasTech_vs_Michigan_0328_tidy = TexasTech_vs_Michigan_0328_tidy[,c(32,1:31)]

#Create timeinterval column
TexasTech_vs_Michigan_0328_tidy$timeinterval = cut(TexasTech_vs_Michigan_0328_tidy$created_at, breaks = "5 min")

#write_as_csv(TexasTech_vs_Michigan_0328_tidy, "TexasTech_vs_Michigan_0328_tidy.csv")
```

##TexasTech_vs_Virginia
```{r TexasTech_vs_Virginia_0408, eval=FALSE}
TexasTech_vs_Virginia_0408 = readRDS("TexasTech_v_Virginia0408.rds")

#Removing unwanted columns
TexasTech_vs_Virginia_0408_tidy = TexasTech_vs_Virginia_0408[,-c(7:12,16:60,67:69,86:88)]

#Adding a column named GameName
TexasTech_vs_Virginia_0408_tidy$GameName = c(rep("TexasTech_vs_Virginia", nrow(TexasTech_vs_Virginia_0408_tidy)))

#Rearranging the columns
TexasTech_vs_Virginia_0408_tidy = TexasTech_vs_Virginia_0408_tidy[,c(32,1:31)]

#Create timeinterval column
TexasTech_vs_Virginia_0408_tidy$timeinterval = cut(TexasTech_vs_Virginia_0408_tidy$created_at, breaks = "5 min")

#write_as_csv(TexasTech_vs_Virginia_0408_tidy, "TexasTech_vs_Virginia_0408_tidy.csv")
```

##TexasTech_vs_MichiganState
```{r TexasTech_vs_MichiganState_0406, eval=FALSE}
TexasTech_vs_MichiganState_0406 = readRDS("Texas_Tech_v_Michigan_State0406.rds")

#Removing unwanted columns
TexasTech_vs_MichiganState_0406_tidy = TexasTech_vs_MichiganState_0406[,-c(7:12,16:60,67:69,86:88)]

#Adding a column named GameName
TexasTech_vs_MichiganState_0406_tidy$GameName = c(rep("TexasTech_vs_MichiganState", nrow(TexasTech_vs_MichiganState_0406_tidy)))

#Rearranging the columns
TexasTech_vs_MichiganState_0406_tidy = TexasTech_vs_MichiganState_0406_tidy[,c(32,1:31)]

#Create timeinterval column
TexasTech_vs_MichiganState_0406_tidy$timeinterval = cut(TexasTech_vs_MichiganState_0406_tidy$created_at, breaks = "5 min")

#write_as_csv(TexasTech_vs_MichiganState_0406_tidy, "TexasTech_vs_MichiganState_0406_tidy.csv")
```

##Purdue_vs_Virginia
```{r Purdue_vs_Virginia_0330, eval=FALSE}
Purdue_vs_Virginia_0330 = readRDS("Purdue_v_Virginia_0330.rds")

#Removing unwanted columns
Purdue_vs_Virginia_0330_tidy = Purdue_vs_Virginia_0330[,-c(7:12,16:60,67:69,86:88)]

#Adding a column named GameName
Purdue_vs_Virginia_0330_tidy$GameName = c(rep("Purdue_vs_Virginia", nrow(Purdue_vs_Virginia_0330_tidy)))

#Rearranging the columns
Purdue_vs_Virginia_0330_tidy = Purdue_vs_Virginia_0330_tidy[,c(32,1:31)]

#Create timeinterval column
Purdue_vs_Virginia_0330_tidy$timeinterval = cut(Purdue_vs_Virginia_0330_tidy$created_at, breaks = "5 min")

#write_as_csv(Purdue_vs_Virginia_0330_tidy, "Purdue_vs_Virginia_0330_tidy.csv")
```

##Combining data
```{r combining all seven dataframes, eval=FALSE}
Combined_data = full_join(Auburn_vs_Kentucky_0331_tidy, Auburn_vs_Virginia_0406_tidy, by = colnames(Auburn_vs_Kentucky_0331_tidy))

Combined_data1 = full_join(TexasTech_vs_Michigan_0328_tidy, VirginiaTech_vs_Duke_0329_tidy, by = colnames(VirginiaTech_vs_Duke_0329_tidy))

Combined_data2 = full_join(Combined_data,Combined_data1, by = colnames(Combined_data))

Combined_data3 = full_join(TexasTech_vs_Virginia_0408_tidy, TexasTech_vs_MichiganState_0406_tidy, by = colnames(TexasTech_vs_MichiganState_0406_tidy))

Combined_data4 = full_join(Purdue_vs_Virginia_0330_tidy, Combined_data3, by = colnames(Combined_data3))

Final_data = full_join(Combined_data2, Combined_data4, by = colnames(Combined_data4))

Final_data$numeric_timeinterval = as.POSIXct(Final_data$timeinterval)
#write_as_csv(Final_data, "Final_data.csv")

#Final_data = read_twitter_csv("/Users/dodo/Desktop/datas/Final_data.csv")
```



### WORD CLOUD SECTION ###

```{r functions, eval=FALSE}
#Removes URL
removeURL = function(x) gsub("?(f|ht)(tp)(s?)(://)(.*)[.|/](.*)+", "", x)

#Removes Mentions
removeMentions = function(x) str_replace(x, pattern = "(?<=@)[:graph:]*", replacement = "")

#Removes the word RT
removeRT = function(x) str_replace(x, pattern = "RT", replacement = "")

#Removes special characters
removeSpecial = function(x) iconv(x, "latin1", "ASCII", sub="")

#Changes the word into its root word.
rootWord = function(x){
  sapply(x, FUN = function(i) i %>% hunspell_parse %>% unlist %>%
                         hunspell_stem(dict = dictionary("en_GB")) %>%
                         do.call(paste, .)) %>% 
    lapply(FUN = function(i) i[1]) %>% unlist
}
```



###        RUNNING CODE FOR INDIVIDUAL GAMES       ###

#Auburn_vs_Kentucky_0331
```{r tweets_Auburn_vs_Kentucky_0331_tidy, eval=FALSE}
corpus = as.character(Auburn_vs_Kentucky_0331_tidy$text) %>%
  tolower() %>%
  removeURL %>%
  rootWord %>%
  removeSpecial %>%
  VectorSource %>%
  VCorpus

cleaned_corpus = tm_map(corpus, tolower) %>%
  tm_map(PlainTextDocument) %>%
  tm_map(removePunctuation) %>%
  tm_map(removeNumbers) %>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(stripWhitespace)

#Document Term Matrix
DTM = DocumentTermMatrix(cleaned_corpus) %>% 
  removeSparseTerms(0.99) %>%
  as.matrix

#Coerce the matrix into a dataframe
DTM_df = as.data.frame(DTM)

#Collapsing the columns
wordcount = as.data.frame(colSums(DTM_df))

#Adding a column called words for the wordcloud function to work
wordcount$words = row.names(wordcount)

#Rearranging the columns for the wordcloud function to work. 
wordcount_Auburn_vs_Kentucky_0331 = wordcount[,c(2,1)]

#Adding a column called GameName
wordcount_Auburn_vs_Kentucky_0331$GameName = c(rep("Auburn_vs_Kentucky", nrow(wordcount_Auburn_vs_Kentucky_0331)))
```

#Auburn_vs_Virginia_0406
```{r tweets_Auburn_vs_Virginia_0406_tidy, eval=FALSE}
corpus = as.character(Auburn_vs_Virginia_0406_tidy$text) %>%
  tolower() %>%
  removeURL %>%
  rootWord %>%
  removeSpecial %>%
  VectorSource %>%
  VCorpus

cleaned_corpus = tm_map(corpus, tolower) %>%
  tm_map(PlainTextDocument) %>%
  tm_map(removePunctuation) %>%
  tm_map(removeNumbers) %>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(stripWhitespace)

#Document Term Matrix
DTM = DocumentTermMatrix(cleaned_corpus) %>% 
  removeSparseTerms(0.99) %>%
  as.matrix

#Coerce the matrix into a dataframe
DTM_df = as.data.frame(DTM)

#Collapsing the columns
wordcount = as.data.frame(colSums(DTM_df))

#Adding a column called words for the wordcloud function to work
wordcount$words = row.names(wordcount)

#Rearranging the columns for the wordcloud function to work. 
wordcount_Auburn_vs_Virginia_0406 = wordcount[,c(2,1)]

#Adding a column called GameName
wordcount_Auburn_vs_Virginia_0406$GameName = c(rep("Auburn_vs_Virginia", nrow(wordcount_Auburn_vs_Virginia_0406)))
```

#Purdue_vs_Virginia_0330
```{r tweets_Purdue_vs_Virginia_0330_tidy, eval=FALSE}
corpus = as.character(Purdue_vs_Virginia_0330_tidy$text) %>%
  tolower() %>%
  removeURL %>%
  rootWord %>%
  removeSpecial %>%
  VectorSource %>%
  VCorpus

cleaned_corpus = tm_map(corpus, tolower) %>%
  tm_map(PlainTextDocument) %>%
  tm_map(removePunctuation) %>%
  tm_map(removeNumbers) %>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(stripWhitespace)

#Document Term Matrix
DTM = DocumentTermMatrix(cleaned_corpus) %>% 
  removeSparseTerms(0.99) %>%
  as.matrix

#Coerce the matrix into a dataframe
DTM_df = as.data.frame(DTM)

#Collapsing the columns
wordcount = as.data.frame(colSums(DTM_df))

#Adding a column called words for the wordcloud function to work
wordcount$words = row.names(wordcount)

#Rearranging the columns for the wordcloud function to work. 
wordcount_Purdue_vs_Virginia_0330 = wordcount[,c(2,1)]

#Adding a column called GameName
wordcount_Purdue_vs_Virginia_0330$GameName = c(rep("Purdue_vs_Virginia", nrow(wordcount_Purdue_vs_Virginia_0330)))
```

#TexasTech_vs_Michigan_0328
```{r tweets_TexasTech_vs_Michigan_0328_tidy, eval=FALSE}
corpus = as.character(TexasTech_vs_Michigan_0328_tidy$text) %>%
  tolower() %>%
  removeURL %>%
  rootWord %>%
  removeSpecial %>%
  VectorSource %>%
  VCorpus

cleaned_corpus = tm_map(corpus, tolower) %>%
  tm_map(PlainTextDocument) %>%
  tm_map(removePunctuation) %>%
  tm_map(removeNumbers) %>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(stripWhitespace)

#Document Term Matrix
DTM = DocumentTermMatrix(cleaned_corpus) %>% 
  removeSparseTerms(0.99) %>%
  as.matrix

#Coerce the matrix into a dataframe
DTM_df = as.data.frame(DTM)

#Collapsing the columns
wordcount = as.data.frame(colSums(DTM_df))

#Adding a column called words for the wordcloud function to work
wordcount$words = row.names(wordcount)

#Rearranging the columns for the wordcloud function to work. 
wordcount_TexasTech_vs_Michigan_0328 = wordcount[,c(2,1)]

#Adding a column called GameName
wordcount_TexasTech_vs_Michigan_0328$GameName = c(rep("TexasTech_vs_Michigan", nrow(wordcount_TexasTech_vs_Michigan_0328)))
```

#TexasTech_vs_MichiganState_0406
```{r tweets_TexasTech_vs_MichiganState_0406_tidy, eval=FALSE}
corpus = as.character(TexasTech_vs_MichiganState_0406_tidy$text) %>%
  tolower() %>%
  removeURL %>%
  rootWord %>%
  removeSpecial %>%
  VectorSource %>%
  VCorpus

cleaned_corpus = tm_map(corpus, tolower) %>%
  tm_map(PlainTextDocument) %>%
  tm_map(removePunctuation) %>%
  tm_map(removeNumbers) %>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(stripWhitespace)

#Document Term Matrix
DTM = DocumentTermMatrix(cleaned_corpus) %>% 
  removeSparseTerms(0.99) %>%
  as.matrix

#Coerce the matrix into a dataframe
DTM_df = as.data.frame(DTM)

#Collapsing the columns
wordcount = as.data.frame(colSums(DTM_df))

#Adding a column called words for the wordcloud function to work
wordcount$words = row.names(wordcount)

#Rearranging the columns for the wordcloud function to work. 
wordcount_TexasTech_vs_MichiganState_0406 = wordcount[,c(2,1)]

#Adding a column called GameName
wordcount_TexasTech_vs_MichiganState_0406$GameName = c(rep("TexasTech_vs_MichiganState", nrow(wordcount_TexasTech_vs_MichiganState_0406)))
```

#TexasTech_vs_Virginia_0408
```{r tweets_TexasTech_vs_Virginia_0408_tidy, eval=FALSE}
corpus = as.character(TexasTech_vs_Virginia_0408_tidy$text) %>%
  tolower() %>%
  removeURL %>%
  rootWord %>%
  removeSpecial %>%
  VectorSource %>%
  VCorpus

cleaned_corpus = tm_map(corpus, tolower) %>%
  tm_map(PlainTextDocument) %>%
  tm_map(removePunctuation) %>%
  tm_map(removeNumbers) %>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(stripWhitespace)

#Document Term Matrix
DTM = DocumentTermMatrix(cleaned_corpus) %>% 
  removeSparseTerms(0.99) %>%
  as.matrix

#Coerce the matrix into a dataframe
DTM_df = as.data.frame(DTM)

#Collapsing the columns
wordcount = as.data.frame(colSums(DTM_df))

#Adding a column called words for the wordcloud function to work
wordcount$words = row.names(wordcount)

#Rearranging the columns for the wordcloud function to work. 
wordcount_TexasTech_vs_Virginia_0408 = wordcount[,c(2,1)]

#Adding a column called GameName
wordcount_TexasTech_vs_Virginia_0408$GameName = c(rep("TexasTech_vs_Virginia", nrow(wordcount_TexasTech_vs_Virginia_0408)))
```

#VirginiaTech_vs_Duke_0329
```{r tweets_VirginiaTech_vs_Duke_0329_tidy, eval=FALSE}
corpus = as.character(VirginiaTech_vs_Duke_0329_tidy$text) %>%
  tolower() %>%
  removeURL %>%
  rootWord %>%
  removeSpecial %>%
  VectorSource %>%
  VCorpus

cleaned_corpus = tm_map(corpus, tolower) %>%
  tm_map(PlainTextDocument) %>%
  tm_map(removePunctuation) %>%
  tm_map(removeNumbers) %>%
  tm_map(removeWords, stopwords("english")) %>%
  tm_map(stripWhitespace)

#Document Term Matrix
DTM = DocumentTermMatrix(cleaned_corpus) %>% 
  removeSparseTerms(0.99) %>%
  as.matrix

#Coerce the matrix into a dataframe
DTM_df = as.data.frame(DTM)

#Collapsing the columns
wordcount = as.data.frame(colSums(DTM_df))

#Adding a column called words for the wordcloud function to work
wordcount$words = row.names(wordcount)

#Rearranging the columns for the wordcloud function to work. 
wordcount_VirginiaTech_vs_Duke_0329 = wordcount[,c(2,1)]

#Adding a column called GameName
wordcount_VirginiaTech_vs_Duke_0329$GameName = c(rep("VirginiaTech_vs_Duke", nrow(wordcount_VirginiaTech_vs_Duke_0329)))
```

```{r write-as-csv, eval=FALSE}
write.csv(wordcount_Auburn_vs_Kentucky_0331, "wordcount_Auburn_vs_Kentucky_0331.csv")
write.csv(wordcount_Auburn_vs_Virginia_0406, "wordcount_Auburn_vs_Virginia_0406.csv")
write.csv(wordcount_Purdue_vs_Virginia_0330, "wordcount_Purdue_vs_Virginia_0330.csv")
write.csv(wordcount_TexasTech_vs_Michigan_0328, "wordcount_TexasTech_vs_Michigan_0328.csv")
write.csv(wordcount_TexasTech_vs_MichiganState_0406, "wordcount_TexasTech_vs_MichiganState_0406.csv")
write.csv(wordcount_TexasTech_vs_Virginia_0408, "wordcount_TexasTech_vs_Virginia_0408.csv")
write.csv(wordcount_VirginiaTech_vs_Duke_0329, "wordcount_VirginiaTech_vs_Duke_0329.csv")
```

#Comibining the wordcount dataframes into a single dataframe. 
```{r wordcount_combined, eval=FALSE}
wordcount_combined = full_join(wordcount_Auburn_vs_Kentucky_0331,wordcount_Auburn_vs_Virginia_0406, by = colnames(wordcount_Auburn_vs_Virginia_0406)) %>%
  full_join(., wordcount_Purdue_vs_Virginia_0330, by = colnames(wordcount_Purdue_vs_Virginia_0330)) %>%
  full_join(., wordcount_TexasTech_vs_Michigan_0328, by = colnames(wordcount_TexasTech_vs_Michigan_0328)) %>%
  full_join(., wordcount_TexasTech_vs_MichiganState_0406, by = colnames(wordcount_TexasTech_vs_MichiganState_0406)) %>%
  full_join(., wordcount_TexasTech_vs_Virginia_0408, by = colnames(wordcount_TexasTech_vs_Virginia_0408)) %>%
  full_join(., wordcount_VirginiaTech_vs_Duke_0329, by = colnames(wordcount_VirginiaTech_vs_Duke_0329))

write.csv(wordcount_combined, "wordcount_combined.csv")
```







